Rubin Observatory Scheduling Algorithm and Simulations

### 2022-09-07 ms.tex

%\correspondingauthor{August Muench}
%\email{greg.schwarz@aas.org, gus.muench@aas.org}

@@

@@

Elah's paper \citet{Naghib2019}, Daniel's paper \citep{Rothchild2019}

@@

Sky brightness paper \citep{Yoachim2016}

@@

XXX--I think this is one potential sequence per night, and then we place it at the optimal time in the night?

@@

>>>>

\correspondingauthor{Peter Yoachim}
\email{yoachim@uw.edu}

@@

\author[0000-0001-5916-0031]{R. Lynne Jones}
\affiliation{Department of Astronomy and the DiRAC Institute, University of Washington, Seattle, WA 98195, USA}

\author[0000-0002-7357-0317]{Eric H. Neilsen}
\affiliation{Fermi National Accelerator Laboratory, P.O. Box 500, Batavia, IL 60510, USA)}

\author{Tiago Ribeiro}
\affiliation{Vera C. Rubin Observatory (United States)}

\author[0000-0001-5250-2633]{\v{Z}eljko Ivezi\'{c}}
\affiliation{Department of Astronomy and the DiRAC Institute, University of Washington, Seattle, WA 98195, USA}

@@

Elahe's paper \citet{Naghib2019}, Daniel's paper \citep{Rothchild2019}

@@

\sunbsection{Kinematic Model}

Run through the kinematic model. Which motions are modeled, cable wrap tracked, etc.

including scheduled and unscheduled downtime

\subsection{Environmental Models}
Seeing, weather, sky brightness

We have three definitions of ``seeing". The full width half maximum of a star at zenith at 500 nm ($FWHM_{500}$), the geometric full width at half maximum ($FWHM_{geom}$), and the effective FWHM ($FWHM_{eff}$).

\begin{equation}
    FWHM_{geom} = 0.822 FWHM_{eff} + 0.052\arcsec
\end{equation}

Looks like we have a wavelength correction of $(\lambda_{raw}/\lambda_{filter})^{0.3}$

and airmass correction of $X^{0.6}$

For clouds, we assume that observations are not possible if more than 30\% of the sky is cloudy. This level is reached 28\% of the time. XXX-mention how this compares to other weather downtimes. Ugh, now I can't find that nice SOAR page that had a nice table.

Sky brightness paper \citep{Yoachim2016}.

@@

XXX--I think this is one potential sequence per night, and then we place it at the optimal time in the night? maybe add a plot of the desired and best fit cumulative observation count.

@@

For the majority of observations we use a modified Markov Decision Process (MDP), similar to the one developed in \citet{Naghib2019}.

An MDP has the advantage of being able to encapsulate common astronomical observing rules of thumb into a small number of basis functions.

xxx-maybe make a plot of the baseline tesselation that gets randomized.
